Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-17 ms.Rnw
Reduced size of saved data

# First, we need to simulate the epidemic model using the fitted parameters.
registerDoRNG(18599687)
foreach(
  i = 1:length(lee1_epi_mif),
  .combine = rbind
) %dopar% {
  guess <- coef(lee1_epi_mif)
  sims <- simulate(h1_epi, nsim = N_LEE_SIMS, format = 'data.frame',
                   params = guess)  # 20 sims for each set of parameters
  sims$param_set <- i
  sims
} -> all_sims

@@

h1_end <- haiti1(period = "endemic")
start_states <- all_sims %>% filter(week == max(week))

@@

        start_states %>%
          filter(param_set == i) %>%
          select(-.id, -week, -param_set) %>%
          sapply(., median, na.rm = TRUE) -> rinit_parms

@@

rm(
  lee_end_ll, lee_epi_ll, h1_end, h1_epi, all_sims, end_start,
  N_LEE_SIMS, N_PARAMS, NMIF, NP_EVAL, NP_MIF, NREPS_EVAL
)
gc()
@

>>>>

# First, we need to simulate the epidemic model using the fitted parameters.
registerDoRNG(18599687)
foreach(
  i = 1:length(lee1_epi_mif),
  .combine = rbind
) %dopar% {
  guess <- coef(lee1_epi_mif)
  sims <- simulate(
    h1_epi,
    nsim = N_LEE_SIMS,
    format = 'data.frame',
    params = guess
  )  %>%
    dplyr::filter(week == max(week)) %>%
    dplyr::select(-.id, -week)

  sims$param_set <- i
  sims
} -> start_states

@@

h1_end <- haiti1(period = "endemic")

@@

        start_states %>%
          filter(param_set == i) %>%
          select(-param_set) %>%
          sapply(., median, na.rm = TRUE) -> rinit_parms

@@

rm(
  lee_end_ll, lee_epi_ll, h1_end, h1_epi, end_start,
  N_LEE_SIMS, N_PARAMS, NMIF, NP_EVAL, NP_MIF, NREPS_EVAL
)
gc()
@
